\documentclass[]{Keenan-Nicholson-Resume}
\fullname{Keenan Nicholson}
\jobtitle{Software Developer \& GIS Analyst}

\begin{document}
\resumeheader
{\linkedin{kbnicholson/}{linkedin.com/in/kbnicholson/}}
{\email{keenanbnicholson@gmail.com}{keenanbnicholson@gmail.com}}
{\github{Keenan-Nicholson}{github.com/Keenan-Nicholson}}
{\phone{+1 709-649-8326}{+1 709-649-8326}}
{\website{keenannicholson.me/}{keenannicholson.me/}}

\begin{section}{Education}
    \begin{subsection}{Bachelor of Arts}{Major in Computer Science, minor in Geography}{Memorial University of Newfoundland}{Jan 2021 -- Dec 2023}
    \end{subsection}
    \begin{subsection}{Bachelor of Science}{Major in Computational Mathematics}{Memorial University of Newfoundland}{Sep 2016 -- Apr 2020}
    \end{subsection}
\end{section}

\begin{section}{Work Experience (selected)}
    \begin{subsection}{C-CORE}{Image Analyst}{Apr 2023 -- Sep 2023}{St. John's, NL}
        \item Data driven full-stack development of web applications
        \vspace{-4pt}
            \begin{itemize}[itemsep=-6.5pt]
                \item Frontend: React.js, HTML, CSS, Material UI (MUI), and Chakra UI.
                \item Backend: Python, Pandas, SpatioTemporal Asset Catalogs (STAC)
            \end{itemize}
        \vspace{1pt}
        \item Analyzing satellite imagery using technologies such as ArcGIS Pro, Python, Pandas, and Matplotlib to \newline monitor iceberg and river ice activity.
    \end{subsection}

    \begin{subsection}{Memorial University of Newfoundland}{Research Assistant}{Jan 2019 -- May 2019}{Corner Brook, NL}
        \item I received a full-time work grant from NSERC. During that time, I researched the properties of algebraic groups as codes and developed an algorithm to decode twisted permutation codes. These codes demonstrate improved reliability and reduced minimum distance compared to other codes in specific scenarios.
    \end{subsection}
\end{section}

\begin{section}{Projects}
\begin{subsectionnobullet}{Social Media Hiking App}{Personal Project}{Work in Progress}{}
    \item{I am actively working on an application that enables users to share their outdoor adventure experiences by uploading .gpx files. The current stage of development involves a backend system that converts and uploads these .gpx files into a PostGIS database. These uploaded adventures are then displayed on an interactive map. Currently, I am in the process of implementing user authentication and login functionalities.

    In the upcoming phases of the project, I plan to establish friendship connections between users, allowing them to interact by liking and commenting on each other's adventure posts. \href{https://github.com/Keenan-Nicholson/hiking-app}{https://github.com/Keenan-Nicholson/hiking-app}.}
        \vspace{-4pt}
        \begin{itemize}[itemsep=-6.5pt]
            \item Frontend: React.js, HTML, CSS.
            \item Backend: Python, GeoPandas, FastAPI, TiPg, Postgres (PostGIS).
        \end{itemize}
\end{subsectionnobullet}

\begin{subsectionnobullet}{ISS Tracker Twitter Bot}{Personal Project}{May 2022}{}
    \item{This application implements Cheerio and node-fetch libraries to scrape real-time International Space Station location data from NASA's website. It then formats and utilizes the Twit library to tweet the ISS visibility details for specific cities in Newfoundland and Labrador. \href{https:\\github.com/Keenan-Nicholson/ISS_Twitter_Bot}{https://github.com/Keenan-Nicholson/ISS\_Twitter\_Bot}.}
\end{subsectionnobullet}

\end{section}

\sectiontable{Technical skills}{
    \entry{Programming Languages}{JavaScript / TypeScript, Python, HTML, CSS}
    \entry{GIS}{ArcGIS Pro, QGIS, GeoPandas, SpatioTemporal Asset Catalogs (STAC)}
    \entry{Frameworks}{React.js, Chakra UI, Material UI}
    \entry{Operating Systems}{Windows, MAC, Linux}
}

\end{document}
